### 2017-07-19 background.tex
Fixing some phrases and wording

There are two major approaches that attempt to solve the problem of computing on sensitive
datasets without disclosing micro-data: data enclaves and formal privacy techniques. Data enclaves attempt to
provide a secure environment that enable computation over sensitive data with security enforcement
to control what enters and exits the system often requiring human oversight. Formal privacy
techniques on the other hand state privacy assumptions and guarantees and the privacy loss
from analyses are formally defined.

\kyle{Any citations for the following}
Formal privacy techniques such as homomorphic encryption, secure multiparty computation, and
other cryptographic solutions for protecting private data often require significant computational
overhead ~\cite{gentry2012fully} \cite{naehrig2011can}. Prior work on database based solutions \cite{popa2011cryptdb}
demonstrates the need for matching the privacy protecting methods used to the analysis in question
to reduce overheads. The majority of the work in this area is focused on the security of
numerical data, while the data we are dealing with is mostly large volumes of textual data.
Recent approaches for applying privacy techniques to securely compute
mathematical operations at large scale incur a 2x overhead~\cite{kepner2014computing}.

Computing systems in some of the most critical and sensitive areas such as military, avionics,
and nuclear energy are protected from intrusion by physical isolation~\cite{byres2013air, ross2013security}.
For example, the U.S. Census Bureau operates several enclaves that host sensitive micro-data accessible
only on site~\cite{rdc_uscensus}. Due to the limitations of physical proximity, data enclaves
have evolved to support network access via encrypted channels and limited bandwidth~\cite{lane2008using, grossman2016toward}.
Accessibility in this case comes at the cost of increased attack surface. Such systems, while
capable of limiting the extent to which data can be viewed, cannot protect against say a single
sensitive line of micro-data being viewed over a secure remote session. They depend on non-disclosure
agreements with users to prevent such information from being divulged.

Traditionally data enclaves are hosted privately using on-premise infrastructure. As 
such they often require significant upfront investment (e.g. physical infrastructure) and reoccurring costs 
from the personnel required to operate the infrastructure as well as develop and maintain custom software. 
They are also often limited in their ability to scale
compute capabilities in response to requirements. In many cases an on-premise data enclave is far from ideal
when considering distributed research teams, large-scale data anlaytics, and highly sporadic
usage patterns common in data science. Instead, cloud hosted data enclaves offer scalability,
democratize access to capabilities, and can support distributed collaborations. 
 %terms of enabling anyone to host a secure data enclave and collaborate safely with a
%distributed set of peers.

>>>>

There are two major approaches that attempt to solve the problem of computing on sensitive
datasets without disclosing micro-data: data enclaves and formal privacy techniques. Data enclaves attempt to
provide an environment that enables computation over sensitive data with security enforced
at the perimeter, contolling what enters and exits the system, often requiring human oversight.
Formal privacy techniques on the other hand state privacy assumptions and guarantees and the privacy loss
from analyses are formally defined.

\kyle{Any citations for the following}
Formal privacy techniques such as homomorphic encryption, secure multiparty computation, and
other cryptographic solutions for protecting private data often require significant computational
overhead ~\cite{gentry2012fully} \cite{naehrig2011can}. Prior work on database based solutions
\cite{popa2011cryptdb} demonstrate the need for matching the privacy protecting techniques to the type of
numerical analyses in question to reduce overheads. Recent approaches for applying privacy techniques to
securely compute mathematical operations at large scale incur a 2x overhead~\cite{kepner2014computing}.
The majority of the work in this area is focused on the security of numerical data, while the datasets
we focus on are mostly large volumes of unstructured and textual data.

Computing systems in some of the most critical and sensitive areas such as military, avionics,
and nuclear energy are protected from intrusion by physical isolation~\cite{byres2013air, ross2013security}.
For example, the U.S. Census Bureau operates several enclaves that host sensitive micro-data accessible
only on site~\cite{rdc_uscensus}. To overcome the limitations of physical proximity, data enclaves
have evolved to support network access via encrypted channels and limited bandwidth~\cite{lane2008using, grossman2016toward}.
Accessibility in this case comes at the cost of increased attack surface. Such systems, while
capable of limiting the extent to which data can be viewed, cannot protect against say a single
sensitive line of micro-data being viewed over a secure remote session. They depend on non-disclosure
agreements with users to prevent such information from being divulged.

Traditionally data enclaves are hosted privately using on-premise infrastructure. As 
such they often require significant upfront investment (e.g. physical infrastructure) and reoccurring costs 
from the personnel required to operate the infrastructure as well as develop and maintain custom software. 
They are also often limited in their ability to scale
compute capabilities in response to requirements. In many cases an on-premise data enclave is far from ideal
when considering distributed research teams, large-scale data anlaytics, and highly sporadic
usage patterns common in data science. Instead, cloud hosted data enclaves offer scalability,
democratize access to capabilities, and support distributed collaborations. 
 %terms of enabling anyone to host a secure data enclave and collaborate safely with a
%distributed set of peers.
